Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-02 ms.tex
figure order (still wrong)

For the other orbital phases, we binned the light curve (with systematics removed) in eight intervals of about 0.1 in orbital phase, with endpoints at phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These endpoints were chosen to ensure that there is no contribution from in-transit or in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin. To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the $3.6\mu$m data, we also add red noise on the timescale of a phase bin, following \cite{pont06}.  The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also show a 100 ppm error bar in the lower right of each panel to draw attention to the changing limits on the y-axes.}}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{fig7.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM. We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig8.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).} 
\label{fig:dayside}
\end{figure*}

@@

\subsection{Transmission Spectrum}
Each phase curve observation includes a transit of WASP-103b. To measure the wavelength-dependent transit depths (the transmission spectrum), we select a subset of each phase curve. The subset includes the transit and additional baseline on either side, such that the total light curve has twice the duration of the transit. Over this short duration, there is negligible curvature in the light curve due to the planet's thermal phase variation. We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter. The orbital parameters (inclination, $a/R_s$, period, and time of central transit) were fixed at previously published values listed in \S\,\ref{sec:fits}. We fit for the instrument systematics using the same model as for the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration). The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled.

We show the measured transmission spectrum in Figure\,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the average nightside planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux using a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146. We assume a nightside temperature of 1700 K, which is near the median of the nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}). We also show the uncorrected transit depths. The corrected and uncorrected transit depths are listed in Table\,\ref{table:tspec}. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of more than five atmospheric scale heights.  The uncorrected spectrum is inconsistent with a flat line at $3.2\,\sigma$ confidence, whereas the nightside-corrected spectrum is consistent within $1\,\sigma$.  The corrected spectrum is also consistent with predictions from the $\tau_\mathrm{drag4}$ GCM, which shows water features in the WFC3 bandpass. Future observations with higher precision could reveal these features. %The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.  Of these, only the 2000 K model yields a transit depth consistent with the measurement of \cite{lendl17} at shorter wavelengths where nightside contamination is negligible ($1.3092 \pm 0.0114$\%). FIXME: could we see water at higher precision?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig9.pdf}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM, with squares indicating the model binned over the \Spitzer\ bandpasses. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}

\begin{deluxetable}{LLL}
\tablecolumns{3}
\tablewidth{0pt}
\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}
\tablehead{
\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\
\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}
\startdata
1.175 & 1.329049 \pm 0.000092 & 0.013228 \pm 0.000092 \\
1.225 & 1.329408 \pm 0.000087 & 0.013217 \pm 0.000087 \\
1.275 & 1.333837 \pm 0.000086 & 0.013246 \pm 0.000086 \\
1.325 & 1.334184 \pm 0.000087 & 0.013233 \pm 0.000087 \\
1.375 & 1.359366 \pm 0.000089 & 0.013467 \pm 0.000089 \\
1.425 & 1.353629 \pm 0.000091 & 0.013390 \pm 0.000091 \\
1.475 & 1.341570 \pm 0.000092 & 0.013249 \pm 0.000092 \\
1.525 & 1.350816 \pm 0.000093 & 0.013319 \pm 0.000093 \\
1.575 & 1.333617 \pm 0.000100 & 0.013125 \pm 0.000100 \\
1.625 & 1.353438 \pm 0.000104 & 0.013299 \pm 0.000104 \\
3.6 & 1.401322 \pm 0.000328 & 0.013238 \pm 0.000328 \\
4.5 & 1.432949 \pm 0.000264 & 0.013554 \pm 0.000264 \\
\enddata
\vspace{-0.8cm}
\tablecomments{comments}
\end{deluxetable}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig10.pdf}
\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K). The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.  Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
\label{fig:opacities}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig11.pdf}
\caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.  The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).  The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.  The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.  The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.  Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
\label{fig:summary}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig12.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval. The blue lines correspond to solar metallicity (1) and C/O (0.54). The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
\label{fig:composition}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig13.pdf}
\caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species. The thin blue/cyan lines correspond to a sample of randomly drawn nightside TP profiles from the GCM, and the thin red/orange lines correspond to dayside TP profiles. The darker colors (blue/red) indicate the extent of the contribution function (encompassing 80\% of the emitted flux). The thick red and blue lines are the best fit 1D TP profiles for the phase 0.5 (dayside average) and 0.1 (nightside average). The dashed lines are condensation curves for a range of possible cloud species.  The dotted lines correspond to regions of constant H$_2$O abundance, with numbers indicating the log10(H$_2$O volume mixing ratio).}
\label{fig:TP}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig14.pdf}
\caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom). The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag. The models are corrected for the predicted ellipsoidal variability of the planet.}
\label{fig:gcmcomparison}
\end{figure}

\begin{figure*}
	\includegraphics[width = 1.0\textwidth]{fig15.pdf}
	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.  The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth). Rows (2-4) show the abundances of CO, H$_2$O, and H-. At dayside temperatures, water dissociates, so the photospheric water abundance drops by $\sim10$ and the H- abundance increases by $\sim100$. By contrast, the CO abundance is uniform throughout the photosphere.}
\label{fig:GCMabundance}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig16.pdf}
\caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc. The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom). Each row shows spectra from objects of comparable temperature. The dotted gray line corresponds to the best fit blackbody. Effective temperatures are listed in the upper right corners. The wavelength bins used to calculate the water feature amplitude $A_1$ are shaded in gray.}
\label{fig:planetstarcomparison}
\end{figure*}

>>>>

For the other orbital phases, we binned the light curve (with systematics
removed) in eight intervals of about 0.1 in orbital phase, with endpoints at
phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
endpoints were chosen to ensure that there is no contribution from in-transit or
in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from
the mean value of the data points in the bin. To estimate the uncertainty, we
took the standard deviation of the points in the bin and added it in quadrature
to the standard deviation of the data points during secondary eclipse (phase
$0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the
$3.6\mu$m data, we also add red noise on the timescale of a phase bin, following
\cite{pont06}.  The phase-resolved emission spectra are shown in
Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}. We show the
dayside spectrum in Figure\,\ref{fig:dayside}.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only. \added{We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig7.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).} 
\label{fig:dayside}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{fig8.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM. We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

\subsection{Transmission Spectrum}
Each phase curve observation includes a transit of WASP-103b. To measure the
wavelength-dependent transit depths (the transmission spectrum), we select a
subset of each phase curve. The subset includes the transit and additional
baseline on either side, such that the total light curve has twice the duration
of the transit. Over this short duration, there is negligible curvature in the
light curve due to the planet's thermal phase variation. We fit the data with a
transit model, which has free parameters for the planet-to-star radius and a
linear limb darkening parameter. The orbital parameters (inclination, $a/R_s$,
period, and time of central transit) were fixed at previously published values
listed in \S\,\ref{sec:fits}. We fit for the instrument systematics using the
same model as for the phase curve fits, except that we modeled the visit-long
systematic as a linear trend in time (which is sufficient for the shorter
duration). The advantage of fitting the transits separately from the full phase
curves is that the resultant transit depths are not dependent on how the phase
variation is modeled. The transit light curve fits are shown in
Figure\,\ref{fig:transitlc}.

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig9.pdf}
\caption{Best fit transit light curves for WASP-103b (lines), compared to binned data (black points). From top-to-bottom, we show the band-integrated WFC3 light curve, \Spitzer\ 3.6, and $4.5\,\mu$m.}
\label{fig:transitlc}
\end{figure}

We show the measured transmission spectrum in Figure\,\ref{fig:tspec}.  The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the average nightside planet-to-star flux ratio and subtract it from the transit depth. We calculate planet-to-star flux using a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146. We assume a nightside temperature of 1700 K, which is near the median of the nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}). We also show the uncorrected transit depths. The corrected and uncorrected transit depths are listed in Table\,\ref{table:tspec}. For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of more than five atmospheric scale heights.  The uncorrected spectrum is inconsistent with a flat line at $5.3\,\sigma$ confidence, whereas the nightside-corrected spectrum is consistent within $1\,\sigma$.  The corrected spectrum is also consistent with predictions from the $\tau_\mathrm{drag4}$ GCM, which shows water features in the WFC3 bandpass. Future observations with higher precision could reveal these features. %The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.  Of these, only the 2000 K model yields a transit depth consistent with the measurement of \cite{lendl17} at shorter wavelengths where nightside contamination is negligible ($1.3092 \pm 0.0114$\%). FIXME: could we see water at higher precision?

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig10.pdf}
\label{fig:tspec}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM, with squares indicating the model binned over the \Spitzer\ bandpasses. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\end{figure}

\begin{deluxetable}{LLLL}
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}
\tablehead{
\colhead{Wavelength} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{Error}\\
\colhead{(micron)} & \colhead{($T_\mathrm{n} = 0$ K)} & \colhead{($T_\mathrm{n} = 1700$ K)} & \colhead{(\%)}}
\startdata
1.175 & 1.3178 & 1.3115 & 0.0092 \\
1.225 & 1.3144 & 1.3067 & 0.0087 \\
1.275 & 1.3195 & 1.3103 & 0.0086 \\
1.325 & 1.3454 & 1.3345 & 0.0087 \\
1.375 & 1.3512 & 1.3385 & 0.0089 \\
1.425 & 1.3588 & 1.3441 & 0.0091 \\
1.475 & 1.3364 & 1.3197 & 0.0092 \\
1.525 & 1.3522 & 1.3333 & 0.0093 \\
1.575 & 1.3688 & 1.3476 & 0.0100 \\
1.625 & 1.3549 & 1.3314 & 0.0104 \\
3.6 & 1.4013 & 1.3238 & 0.0328 \\
4.5 & 1.4329 & 1.3554 & 0.0264 \\
\enddata
\tablecomments{Wavelength dependent transit depths, corrected for companion dilution and nightside flux (assuming nightside temperatures of 0 and 1700 K for the second and third columns, respectively). The error corresponds to the 68\% credible interval from an MCMC fit to the transit light curves.}
\end{deluxetable}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig11.pdf}
\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K). The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.  Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
\label{fig:opacities}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig12.pdf}
\caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.  The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).  The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.  The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.  The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.  Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
\label{fig:summary}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig13.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval. The blue lines correspond to solar metallicity (1) and C/O (0.54). The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
\label{fig:composition}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig14.pdf}
\caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species. The thin blue/cyan lines correspond to a sample of randomly drawn nightside TP profiles from the GCM, and the thin red/orange lines correspond to dayside TP profiles. The darker colors (blue/red) indicate the extent of the contribution function (encompassing 80\% of the emitted flux). The thick red and blue lines are the best fit 1D TP profiles for the phase 0.5 (dayside average) and 0.1 (nightside average). The dashed lines are condensation curves for a range of possible cloud species.  The dotted lines correspond to regions of constant H$_2$O abundance, with numbers indicating the log10(H$_2$O volume mixing ratio).}
\label{fig:TP}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{fig15.pdf}
\caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom). The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag. The models are corrected for the predicted ellipsoidal variability of the planet.}
\label{fig:gcmcomparison}
\end{figure}

\begin{figure*}
	\includegraphics[width = 1.0\textwidth]{fig16.pdf}
	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.  The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth). Rows (2-4) show the abundances of CO, H$_2$O, and H-. At dayside temperatures, water dissociates, so the photospheric water abundance drops by $\sim10$ and the H- abundance increases by $\sim100$. By contrast, the CO abundance is uniform throughout the photosphere.}
\label{fig:GCMabundance}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{fig17.pdf}
\caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc. The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom). Each row shows spectra from objects of comparable temperature. The dotted gray line corresponds to the best fit blackbody. Effective temperatures are listed in the upper right corners. The wavelength bins used to calculate the water feature amplitude $A_1$ are shaded in gray.}
\label{fig:planetstarcomparison}
\end{figure*}
